---
# This file generates AGENTS.md in the package root.
# It is not part of the package build or the pkgdown site.
# To regenerate it, run from the package root:
#   rmarkdown::render("vignettes/_AGENTS.Rmd", output_file = file.path("AGENTS.md"))
output:
  github_document:
    html_preview: false
params:
  url: "https://raw.githubusercontent.com/insightsengineering/teal/refs/heads/add_common_claude%40main/SHARED_CLAUDE.md"
---
# teal.reporter R Package Development Guide

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package Overview

`teal.reporter` is part of the `teal` framework and provides an API and Shiny modules to manage reporter functionality in a `teal` app.
A report is a set of markup language, code chunks and respective outputs (tables, listings and/or graphs) that can be downloaded
by the user in several formats.
It should also contain data to restore the report on a `teal` application.

It provides 4 main features to the framework:

- Shiny modules with UI and server functions to manage reports on a `teal` session
- `Reporter` manages multiple `teal_card`, which together make up one report
- `teal_card` objects that represent the report of a module in a `teal` application
- `teal_report` object that extends on `teal_data` API by adding API to maintain a representation of the report, in addition to all features `teal_data` and `qenv` already provide
  - See `vignettes/teal-report-class.Rmd` as reference material

## Development Context

The main feature of this package is to provide `teal` apps with reporting capabilities, however it is also intended to allow for extensions, allowing for more data types to be supported as well as custom rendering of the report.

### Relationships with other packages

Direct dependencies:

- `teal.data`: `teal_report` object extends the `teal_data` object by adding `teal_card` slot
  - Any issue with `join_keys` should be addressed in `teal.data`.
- `teal.code`: `teal_data` extends a `qenv` object from `teal.code`, where the code execution and reproducibility features are implemented.
  - Any issue with code execution and reproducibility should be addressed in this package
  - `teal.reporter` extends `eval_code` for `teal_report` so that outputs are added to the `teal_card` automatically (`teal_report-eval_code.R`)

Usage in other framework packages:

- `teal`: uses the API in `teal.reporter` to maintain an instance of the reporter and uses the exported shiny modules for the interface
  - Converts the `data` argument in `teal::init()` function to the `teal_report` object that is used in the modules
- teal module: The `data` argument passed on to modules uses the `teal_report` data type.
  - Automatically tracks the code execution and output objects
  - It is used in custom modules as well as R packages on CRAN: `teal.modules.clinical` and `teal.modules.general`

*Note*: Output objects are captured from the code execution `teal_reporter() |> within(plot(1:10))` will capture a plot.
It is the equivalent to what is being printed on the console when executing code.

### Extending reporter

`teal.reporter` should allow for its functionalities to be extended by users according to their specific needs.
This can be achieved by:

- Extending the `Reporter` class
- Using the `Reporter$set_template()` method that processes each card that is being added
- Adding support for new data types or overwriting existing defaults

`to_rmd()` (exported) and `toHTML()` (generic imported from tools) each have only a `.default` method, which delegates to the internal generics `.to_rmd()` / `.toHTML()`.

- Built-in support for a new class: add `.to_rmd.<class>` / `.toHTML.<class>`. Never add `to_rmd.<class>` inside the package, or users can no longer override it.
Users override by defining or registering `to_rmd.<class>` / `toHTML.<class>`.

This 2 layer dispatch mechanism allows users to overwrite defaults and add their own support for other data types.

```{r teal_content, echo=FALSE, results='asis'}
# Append common shared instructions from teal framework
common_claude_url <- params$url
common_claude_path <- tempfile()
download.file(url = common_claude_url, destfile = common_claude_path, quiet = TRUE)
common_claude_shared <- readLines(common_claude_path)
cat(common_claude_shared, sep = "\n")
```
