---
title: "Comprehensive Overview of Content Blocks in `teal.reporter`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Comprehensive Overview of Content Blocks in teal.reporter}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview of Content Blocks
This document provides a comprehensive overview of all content blocks available in the teal.reporter package.

## Table: Content Blocks in `teal.reporter`

| **Block Type** | **Description** | **Usage Example** |
  |----------------|----------------|-------------------|
  | **`TextBlock`** | Adds text-based content to the report. | ```r\ntext_block <- TextBlock$new(title = "Introduction", content = "This is the introduction to our report.")\n``` |
  | **`PictureBlock`** | Contains graphical content like plots or diagrams. | ```r\npicture_block <- PictureBlock$new(title = "Histogram", file_path = "path/to/histogram.png")\n``` |
  | **`RcodeBlock`** | Embeds R code directly into the report. | ```r\nrcode_block <- RcodeBlock$new(title = "MPG vs HP Plot", r_code = "plot(mtcars$mpg, mtcars$hp, main = 'MPG vs HP')")\n``` |
  | **`NewpageBlock`** | Marks a new page in the report for organization purposes. | ```r\nnew_page <- NewpageBlock$new()\n``` |
  | **`TableBlock`** | Holds and displays tabular data. | ```r\ntable_block <- TableBlock$new(title = "MTCars Data", data = head(mtcars))\n``` |
  | **`ReportCard`** | Combines various content blocks into a single card. | ```r\nreport_card <- ReportCard$new()\nreport_card$append_blocks(list(text_block, picture_block, rcode_block, table_block))\n``` |


## Interaction of Global and Local Echo Options
###Global echo Option
-- Controls whether R code is included globally in the report.
-- Set using options():

```{r}
options(teal.reporter.echo = TRUE)
```
Default: FALSE
###Local echo Option in append_rcode and append_src
-- Controls inclusion of R code at a local level.
append_rcode
```{r}
library(teal.reporter)
report_card <- ReportCard$new()
report_card$append_rcode("plot(mtcars$mpg, mtcars$hp)", echo = TRUE)
```

## Full Example Report
Here's a full example of a report combining all these content blocks:

```{r}

# Set global echo option
options(teal.reporter.echo = TRUE)

# Create individual content blocks
# text_block <- teal.reporter:::TextBlock$new()
# picture_block <- teal.reporter:::PictureBlock$new()
# rcode_block <- teal.reporter:::RcodeBlock$new(r_code = "plot(mtcars$mpg, mtcars$hp, main = 'MPG vs HP')")
# new_page <- teal.reporter:::NewpageBlock$new()
# table_block <- teal.reporter:::TableBlock$new(data = head(mtcars))
# 
# # Create a report card and add blocks
# report_card <- ReportCard$new()
# report_card$append_blocks(list(text_block, picture_block, rcode_block, new_page, table_block))
# 
# # Append specific R code with local echo setting
# report_card$append_rcode(title = "Summary of MPG", r_code = "summary(mtcars$mpg)", echo = TRUE)
# 
# # Preview the report card
# report_card$preview()
# 
# # Add the report card to a report and preview
# report <- Reporter$new()
# report$add_card(report_card)
# report$preview()
```
